---
title: "Homework 5"
author: "Ifrah Fayyaz"
date: "11/11/2021"
output: github_document
---

## Loading libraries:

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
```

# Problem 2

```{r, message=FALSE, warning=FALSE}
prob2 = tibble(
  filename = list.files("./data/")
  )


con_exp = function(path) {
  df = tibble(path %>%
       map_dfr(read_csv))
}

prob2 = prob2 %>%
  mutate(filepath = paste0("./data/", filename)) 

prob2 = prob2 %>%
  mutate(con_exp(prob2$filepath)) %>%
  select(-filepath)
```



dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()








bind_rows(con_exp
          
he = map(
  prob2, bind_rows(
  con_exp(base_url[prob2$files])) %>%
  select(everything())
)


prob2 %>%
  con_exp(files)


%>%
    gather(key = weeks, value = obs, week_1:week_8)
  


check = 
  bind_rows(
    con_exp("./data/con_01.csv"),
    con_exp("./data/con_02.csv"),
    con_exp("./data/con_03.csv")) %>%
  select(everything()) 



ch = map(file_names, con_exp(base_url[file_names$files]))


```


```{r, message=FALSE, warning=FALSE}

```


```{r, message=FALSE, warning=FALSE}

```


```{r, message=FALSE, warning=FALSE}

```


```{r, message=FALSE, warning=FALSE}

```


```{r, message=FALSE, warning=FALSE}

```


```{r, message=FALSE, warning=FALSE}

con_exp = function(path) {
  df =  read_csv(path) %>%
  bind_rows()
  
  df
}

```